### 2018-09-03 Sections/cryptowars.tex
just saving

\comment{To do}
Hacking attacks are related to the weaknesses of an implementation. A first common feature of hacking attacks is that they are feasible, or almost feasible, with present-day technology. 
\subsection{Trojan horse attack}
The best-known example is the family of Trojan horse attacks, in which Eve probes the settings of Alice’s and/or Bob’s devices by sending some light into them and collecting the reflected signal. 
Actually, the first kind of hacking attack that was considered is a form of Trojan horse that would come for free: it was noticed that some photon counters  silicon-based avalanche photodiodes  emit some light at various wavelengths when they detect a photon  Kurtsiefer et al., 2001 . If this light carries some information about which detector has fired, it must be prevented from propagating out, where Eve could detect it.

\subsection{Photon number splitting attack}
\comment{Attacks based on bad implementation rather than bad theory}

\comment{Side-channel attacks}

>>>>

\comment{To do}
Hacking attacks are related to the weaknesses of an implementation. A first common feature of hacking attacks is that they are feasible, or almost feasible, with present-day technology. 
\subsection{Trojan horse attack}
The best-known example is the family of Trojan horse attacks, in which Eve probes the settings of Alice’s and/or Bob’s devices by sending some light into them and collecting the reflected signal. 
Actually, the first kind of hacking attack that was considered is a form of Trojan horse that would come for free: it was noticed that some photon counters  silicon-based avalanche photodiodes  emit some light at various wavelengths when they detect a photon  Kurtsiefer et al., 2001 . If this light carries some information about which detector has fired, it must be prevented from propagating out, where Eve could detect it. 
\subsection{Quantum side channel attacks}

\subsection{Photon number splitting attack}

\cite{PhysRevLett.68.3121}

A beam-splitting (BS)  attack translates the fact that the light that is lost in the channel must be given to Eve: specifically, Eve could be simulating the losses by putting a beam splitter just outside Alice’s laboratory, and then forwarding the remaining photons to Bob on a lossless
line. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels and does not introduce any error.

When the signal can consist of more than one photon, Eve can count the number of photons in each signal and act differently according to the result n of this measure- ment. Such attacks are called photon-number splitting  PNS  attacks
% \comment{Attacks based on bad implementation rather than bad theory}

PNS were discovered as zero-error attacks against BB84 implemented with weak laser pulses; in the typical parameter regime of QKD, even the Poissonian photon-number distribution can be preserved  Lütken- haus and Jahma, 2002 , so that the PNS attack cannot be detected even in principle as long as one known signal intensity is used. Use of different intensities in order to detect PNS attacks is the idea behind the decoy-states method . The distributed-phase-reference protocols also detect PNS attacks.
